\documentclass[12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{macros}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}
\begin{document}
\begin{center}
{\bf Physics 360/Math 360  \ \ MWF 11:00 - 12:00 PM,  Room:  Dennis 231
}
\end{center}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}


\vskip.15in
\noindent\textbf{Instructor:} Michael Lerner,  Dennis 221, Phone: 727-LERNERM
\vskip.15in

\vskip.15in
\noindent\textbf{Assignment 3, Due Friday Jan 30}
\vskip.15in

In this assignment, as in many of the future assignments, we will
investigate a particular topic in depth, rather than solving several
separate problems. This week, we focus on the Legendre polynomials,
which have broad applicability in mathematical physics, especially in
the modeling of spherically symmetric systems.

The text of the following problems is taken (with some small changes)
from Boyce and DiPrima, Chapter 5, section 3.

The following problems deal with the Legendre equation:


\begin{equation}
  \label{L}
  (1-x^2)y'' - 2xy' + \alpha(\alpha+1)y = 0
\end{equation}

As we showed in class, the point $x=0$ is an ordinary point of
\eqref{L}, and the distance from the origin to the nearest zero of
$P(x)=1-x^2$ is 1. Thus the radius of convergence of series solutions
about $x=0$ is at least 1. Also, note that we only need to consider
$\alpha>-1$: if $\alpha \le 1$, make the substitution
$\alpha=(-1+\gamma)$, $\gamma \ge 0$.  Plugging this in gives
$(1-x^2)y'' - 2xy' + \gamma(\gamma+1)y = 0$.

In this problem set, we will examine the solutions of the Legendre
equation, and we will spend some time showing how to write those
solutions in the form that they are typically presented.

\vskip.1in
\textbf{Problem 1} This problem follows the convention of choosing a fundamental set of solutions such that

\begin{align*}
  y_1(x) &= 1 + b_2(x-x_0)^2 + ... \\
  y_2(x) &= (x-x_0) + c_2 (x-x_0)^3 + ... \\
  b_2+c_2 &= a_2
\end{align*}

(Note that these series have already included the fact that one will
be even and one will be odd, a fact that you'll show below.)

We can, of course, use these to build any set of solutions that we'd
like, and it's a particularly convenient convention. Show that two
solutions of the Legendre equation for $|x| < 1$ are

\begin{align*}
  y_1(x) &= 1 - \frac{\alpha(\alpha+1)}{2!}x^2 + \frac{\alpha(\alpha-2)(\alpha+1)(\alpha+3)}{4!}x^4 \\
   &+ \sum_{m=3}^{\infty}(-1)^m\frac{\alpha\cdot\cdot\cdot(\alpha-2m+2)(\alpha+1)\cdot\cdot\cdot(\alpha+2m-1)}{(2m)!}x^{2m}, \\
  y_2(x) &= x - \frac{(\alpha - 1)(\alpha + 2)}{3!}x^3 + \frac{(\alpha-1)(\alpha-3)(\alpha+2)(\alpha+4)}{5!}x^5 \\
  &+ \sum_{m=3}^{\infty}\frac{(\alpha-1)\cdot\cdot\cdot(\alpha-2m+1)(\alpha+2)\cdot\cdot\cdot(\alpha+2m)}{(2m+1)!}x^{2m+1}
\end{align*}

For $y_1$, you must calculate the first several terms. You may do the
proof by induction for the general term for extra credit. For $y_2$,
calculating the first 2-3 terms is sufficient. 

\vskip.1in
\textbf{Problem 2} Show that, if $\alpha$ is zero or a positive even
integer $2n$, the series solution $y_1$ reduces to a polynomial of
degree $2n$ containing only even powers of $x$. Find the polynomials
corresponding to $\alpha=0,2,4$. Similarly, show that if $\alpha$ is a
positive odd integer $2n+1$, the series solution $y_2$ reduces to a
polynomial of degree $2n+1$ containing only odd powers of $x$. Find
the polynomials corresponding to $\alpha=1,3,5$. 

\vskip.1in \textbf{Problem 3} The Legendre polynomial $P_n(x)$ is
defined as the polynomial solution of the Legendre equation with
$\alpha=n$ that also satisfies the condition
$P_n(1)=1$.\\  

\textbf{(a)} Using the results of Problem 2, find the
first five Legendre polynomials, $P_0(x),...,P_5(x)$. \\  

\textbf{(b)}
Plot the graphs of $P_0(x),...,P_5(x)$ in the range for which we've
demonstrated convergence, $|x|\le1$. You may use whatever graphing
package you'd like, including but not limited to Wolfram alpha
(e.g. go to wolframalpha.com and type 
``plot 0.5*(3x\verb|^|2-1) from -1 to
1'' in the box), Matlab, Mathematica, Python+matplotlib, etc. \\

\textbf{(c)} Find the zeros of $P_0(x),...,P_5(x)$.

\vskip.1in
\textbf{Problem 4} \textbf{This problem is only for extra credit; it
  is not required}
It can be shown (you do not need to do this) that the general formula for $P_n(x)$ is

\begin{equation*}
  P_n(x) = \frac{1}{2^n}\sum_{k=0}^{\lfloor n/2 \rfloor} \frac{(-1)^k(2n-2k)!}{k!(n-k)!(n-2k)!}x^{n-2k},
\end{equation*}

where $\lfloor n/2 \rfloor$ (called the floor of $n/2$) denotes the greatest integer less than or equal to $n/2$. By observing the form of $P_n(x)$ for $n$ even and $n$ odd, show that $P_n(-1) = -1^n$

\vskip.1in
\textbf{Problem 5} The Legendre polynomials play an important role in
mathematical physics. For example, solving the potential equation
(Laplace's equation) in spherical coordinates, we encounter the
equation 


\begin{equation*}
  \dd{F(\phi)}{\phi} + \cot\phi\fd{F(\phi)}{\phi} + n(n+1)F(\phi) = 0,\qquad 0 < \phi < \pi
\end{equation*}

Show that the change of variables $x=\cos\phi$ leads to the Legendre
equation with $\alpha=n$ for $y=f(x)=F(\cos^{-1}(x))$ 

Hint: you may need to use the fact that


\begin{equation*}
  \sin(\arccos(x)) = \sqrt{1-x^2};\qquad \cot(\arccos(x)) = \frac{x}{\sqrt{1-x^2}}
\end{equation*}


\vskip.1in
\textbf{Problem 6} \textbf{Just mention the results. No need to
  verify.} Show that for $n=0,1,2,3$, the corresponding Legendre
polynomial is given by the famous Rodrigues formula: 


\begin{equation*}
  P_n(x)=\frac{1}{2^nn!}\frac{d^n}{dx^n}(x^2-1)^n
\end{equation*}

Rodrigues's formula is true for all positive integers $n$, so you may
show the general case instead of the specific cases if you'd
like. Full credit will be given for just verifying the first several terms.

\vskip.1in
\textbf{Problem 7} Show that the Legendre equation can also be written as

\begin{equation*}
  [(1-x^2)y']' = -\alpha(\alpha+1)y
\end{equation*}

It then follows that

\begin{equation}
  \label{e1}
  [(1-x^2)P_n^{'}(x)]' = -n(n+1)P_n(x)
\end{equation}
and
\begin{equation}
  \label{e2}
  [(1-x^2)P_m^{'}(x)]' = -m(m+1)P_m(x).
\end{equation}
By multiplying \eqref{e1} by $P_m(x)$ and \eqref{e2} by $P_n(x)$,
\textbf{integrating by parts}, and then subtracting one equation from the
other, show that


\begin{equation}
  \label{orth}
  \int_{-1}^{1}P_n(x)P_m(x)dx = 0 \qquad \mathrm{if} \quad n \ne m
\end{equation}

This property \eqref{orth} of the Legendre polynomials is known as the
orthogonality property. If $m=n$, it can be shown that the value of
the integral in \eqref{orth} is $2/(2n+1)$. 

\vskip.1in
\textbf{Problem 8} Given a polynomial $f$ of degree $n$, it is possible to express $f$ as a linear combination of $P_0,P_1,...,P_n$:

\begin{equation}
  \label{basis}
  f(x) = \sum_{k=0}^n a_kP_k(x)
\end{equation}

Note that, since the $n+1$ polynomials $P_0,...,P_n$ are linearly
independent, and the degree of $P_k$ is $k$, any polynomial of degree
$n$ can be expressed as \eqref{basis}. \\ Using the result of Problem
7, you can show that 


\begin{equation*}
  a_k=\frac{2k+1}{2}\int_{-1}^1f(x)P_k(x)dx
\end{equation*}

\textbf{but you don't have to! You're done!}

\end{document}
