\documentclass[12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{macros}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}
\begin{document}
\input{header}
\noindent\textbf{Assignment 2, Due Friday Jan 26, 11:00 AM.}
\vskip.15in


The main goal of this part of the class is to get familiar with the
mechanics of working with series and complex numbers. So, this
assignment includes many short problems. The selection below is a good
one to get you acquainted with the techniques. The starred problems
are the ones you're required to turn in (there are ten of them).
\vskip.15in

\noindent\S1.10: 1*,2*,3,4,5 \\
\S1.12: 1* \\
\S1.13: 5ab, 7ab*, 9ab, 10ab, 20* \\
\S1.14: 3* \\
\S1.15: 33* \\
\S2.4: 1*,2,3*,11*,12,13 \\

Additionally, we'll be using iPython Notebooks for several assignments
in the class. Most of you seem comfortable with what we've done in
class.

\begin{itemize}
  \item Install the Anaconda Python Distribution on your
    laptop. Python version 3.something is required. The full
    distribution, rather than MiniConda is better.
  \item If you've never used a programming language before, work
    through the first three CodeAcademy lessons
    (\url{https://www.codecademy.com/learn/learn-python}). Those will get
    you to ``for loops.''
  \item Use a \texttt{for} loop to evaluate the first 4 partial sums
    of one of the series from the previous problems. \textbf{I will
      set aside time in class on Wednesday for answering questions
      related to this, so please do this sooner rather than later!}
\end{itemize}

\end{document}
