\documentclass[12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{macros}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}
\begin{document}
\input{header}
\noindent\textbf{Assignment 4, Due as Tuesday Mar 5}
\vskip.15in


\section{Looking at the Legendre equation: part 2}

\vskip.1in 
\textbf{Problem 4} The Legendre polynomials play an important role in
mathematical physics. For example, solving the potential equation
(Laplace's equation) in spherical coordinates, we encounter the
equation 


\begin{equation*}
  \dd{F(\phi)}{\phi} + \cot\phi\fd{F(\phi)}{\phi} + n(n+1)F(\phi) = 0,\qquad 0 < \phi < \pi
\end{equation*}

Show that the change of variables $x=\cos\phi$ leads to the Legendre
equation with $\alpha=n$ for $y=f(x)=F(\cos^{-1}(x))$ 

Hint: you may need to use the fact that


\begin{equation*}
  \sin(\arccos(x)) = \sqrt{1-x^2};\qquad \cot(\arccos(x)) = \frac{x}{\sqrt{1-x^2}}
\end{equation*}

\vskip.1in 
\noindent\textbf{Problem 5} Show that the Legendre equation can also be written as

\begin{equation*}
  [(1-x^2)y']' = -\alpha(\alpha+1)y
\end{equation*}

It then follows that

\begin{equation}
  \label{e1}
  [(1-x^2)P_n^{'}(x)]' = -n(n+1)P_n(x)
\end{equation}
and
\begin{equation}
  \label{e2}
  [(1-x^2)P_m^{'}(x)]' = -m(m+1)P_m(x).
\end{equation}
By multiplying \eqref{e1} by $P_m(x)$ and \eqref{e2} by $P_n(x)$,
\textbf{integrating by parts}, and then subtracting one equation from the
other, show that


\begin{equation}
  \label{orth}
  \int_{-1}^{1}P_n(x)P_m(x)dx = 0 \qquad \mathrm{if} \quad n \ne m
\end{equation}

This property \eqref{orth} of the Legendre polynomials is known as the
orthogonality property. If $m=n$, it can be shown that the value of
the integral in \eqref{orth} is $2/(2n+1)$. 

\vskip.1in
Given a polynomial $f$ of degree $n$, it is possible to express $f$ as a linear combination of $P_0,P_1,...,P_n$:

\begin{equation}
  \label{basis}
  f(x) = \sum_{k=0}^n a_kP_k(x)
\end{equation}

Note that, since the $n+1$ polynomials $P_0,...,P_n$ are linearly
independent, and the degree of $P_k$ is $k$, any polynomial of degree
$n$ can be expressed as \eqref{basis}. \\ Using the result of Problem
7, you can show that 


\begin{equation*}
  a_k=\frac{2k+1}{2}\int_{-1}^1f(x)P_k(x)dx
\end{equation*}

\textbf{but you don't have to! You're done!}


\section{Boas \S7.2 Wave Review}
Make sure you understand the following problems

1, 6, 7, 17, 21.

(You do not have to turn them in.)

\section{Boas \S7.4 Average Value}
%(Boas \S7.4, Problems \#3, 4, 10, 14) These should be relatively
%fast. Making a quick sketch of the function will make some of
%these trivial. 
For your reference, these are Boas \S7.4 problems \#3, 4, 10 % and 14 
\subsection{} 
Find the average value of the function on the given interval. You may
use equation 4.8 if it applies. It's well worth your time to make a
quick sketch of the function, as you may be able to quickly see
the average value. Especially when it's zero. If you find yourself
spending more than 5 minutes on any one of these, please post to
Piazza asking for hints, and then move on to the next one.

\begin{equation}
  \sin x + 2\sin 2x + 3\sin 3x \qquad \textrm{on} \quad (0,2\pi)
\end{equation}

\subsection{}
\begin{equation}
  1 - e^{-x} \qquad \textrm{on} \quad (0,1)
\end{equation}

\subsection{}
\begin{equation}
  \cos x \qquad \textrm{on} \quad (0,3\pi)
\end{equation}

%%\subsection{}
%%Read through Problem 13. If the result doesn't seem obvious to you,
%%you may prove it and I'll grade it for extra credit. Use the result of
%%Problem 13 to evaluate the following integral without doing any calculation.
%%\begin{equation}
%%  \int_0^{4\pi/3}\sin^2\left(\frac{3x}{2}\right) dx
%%\end{equation}


\section{Boas \S7.5 Fourier Series}

\subsection{}
Problem \S7.5.9 (also graph the sum of the first four non-zero terms using Python in
addition to solving)

\subsection{}
Problem 12.

\subsection{}
For extra credit, you may do problem 13.
%% MGL: this includes hw5.tex

\end{document}
